Ascending the Ladder to Self-Sustainability

### 2022-11-01 onward-2022/onward22-master.tex
Camera-ready corrections / tweaks

\documentclass[sigplan,review]{acmart}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{amsthm}

\acmConference{Onward! Essays}{December 5--10, 2022}{Auckland, New Zealand}

\title{Ascending the Ladder to Self-Sustainability}
\subtitle{Achieving open evolution in an interactive graphical system}
\author{Joel Jakubovic}
\affiliation{\institution{University of Kent} \city{Canterbury} \country{United Kingdom}}
\email{jdj9@kent.ac.uk}
\author{Tomas Petricek}
\affiliation{\institution{Charles University} \city{Prague} \country{Czechia}}
\email{tomas@tomasp.net}

@@

@@

\bibliographystyle{plainurl}
\bibliography{onward22}
\end{document}

>>>>

\documentclass[sigplan,screen]{acmart}
\usepackage[utf8]{inputenc}
%\usepackage[T1]{fontenc}
\usepackage{listings}
\usepackage{hyperref}
\usepackage{amsthm}
%\usepackage{pifont} % For checkmark / cross symbols
\usepackage{microtype}
\usepackage{flushend}

\title{Ascending the Ladder to Self-Sustainability}
\subtitle{Achieving Open Evolution in an Interactive Graphical System}
\author{Joel Jakubovic}
\affiliation{\institution{University of Kent} \city{Canterbury} \country{United Kingdom}}
\email{jdj9@kent.ac.uk}
\author{Tomas Petricek}
\affiliation{\institution{Charles University} \city{Prague} \country{Czechia}}
\email{tomas@tomasp.net}

\setcopyright{acmlicensed}
\acmPrice{15.00}
\acmDOI{10.1145/3563835.3568736}
\acmYear{2022}
\copyrightyear{2022}
\acmSubmissionID{onward22essays-p6-p}
\acmISBN{978-1-4503-9909-8/22/12}
\acmConference[Onward! '22]{Proceedings of the 2022 ACM SIGPLAN International Symposium on New Ideas, New Paradigms, and Reflections on Programming and Software}{December 8--10, 2022}{Auckland, New Zealand}
\acmBooktitle{Proceedings of the 2022 ACM SIGPLAN International Symposium on New Ideas, New Paradigms, and Reflections on Programming and Software (Onward! '22), December 8--10, 2022, Auckland, New Zealand}
\received{2022-09-05}
\received[accepted]{2022-10-03}

@@

\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10011007.10011006.10011066.10011069</concept_id>
       <concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011050</concept_id>
       <concept_desc>Software and its engineering~Context specific languages</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011041.10011048</concept_id>
       <concept_desc>Software and its engineering~Runtime environments</concept_desc>
       <concept_significance>300</concept_significance>
       </concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
\ccsdesc[500]{Software and its engineering~Context specific languages}
\ccsdesc[300]{Software and its engineering~Runtime environments}

\keywords{self-sustaining, self-sustainable, interactive, bootstrapping, visual programming, context-specific, domain-specific}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{onward22}

\end{document}
